Characterizing Stellar Streams by ML

### 2023-07-29 src/tex/ms.tex
[showyourwork] overleaf sync

            \begin{figure*}[h]
                \script{gd1/plot/results.py}
                \centering
                \includegraphics[width=1\linewidth]{figures/gd1/results.pdf}
                \caption{CAPTION}
                TODO:
                \begin{itemize}
                    \item Add plot of the stream linear density
                    \item Reduce the distance between the plot sections
                    \item Color palette for the spur
                    \item more subtle stream MLE path
                    \item weight 5th and 95th percentile distribution
                    \item rerun model with larger pmphi2 sigma
                    \item add the isochrones to the cmd plots
                \end{itemize}
                \label{fig:gd1-results}
            \end{figure*}

            \begin{figure*}
                \centering
                \includegraphics[scale=0.8]{figures-not-syw/gd1/gd1_heatmap_density_KDE2.pdf}
                \caption{Caption}
                \label{fig:gd1-heatmap}
            \end{figure*}

>>>>

            \begin{figure}
                \script{gd1/plot/photometric_background_selection.py}
                \centering
                \includegraphics[width=1\linewidth]{figures/gd1/photometric_background_selection.pdf}
                \caption{Caption}
                \label{fig:gd1-photometric_background_selection}
            \end{figure}

            \begin{figure*}[h]
                \script{gd1/plot/results_full.py}
                \centering
                \includegraphics[width=1\linewidth]{figures/gd1/results_full.pdf}
                \caption{CAPTION}
                TODO:
                \begin{itemize}
                    \item Add plot of the stream linear density
                    \item Reduce the distance between the plot sections
                    \item Color palette for the spur
                    \item more subtle stream MLE path
                    \item weight 5th and 95th percentile distribution
                    \item rerun model with larger pmphi2 sigma
                    \item add the isochrones to the cmd plots
                \end{itemize}
                \label{fig:gd1-results-full}
            \end{figure*}

            \begin{figure*}[h]
                \script{gd1/plot/results_panels.py}
                \centering
                \includegraphics[width=1\linewidth]{figures/gd1/results_panels.pdf}
                \caption{CAPTION}
                \label{fig:gd1-results-panels}
            \end{figure*}

            \begin{figure*}
                \script{gd1/plot/smooth_likelihood.py}
                \centering
                \includegraphics[scale=0.8]{figures/gd1/smooth_likelihood.pdf}
                \caption{Caption}
                \label{fig:gd1-heatmap}
            \end{figure*}
